Analyses of 27 years of stand structure development and basal area growth response to a range of initial basal area density levels, 1992-2019

### 2020-10-17 manuscript/EP1162_manuscript_draft.Rmd
manny edits

@@

# Captions
appNums(name="piInitRaw",display=FALSE)
appNums(name="piPCTInitRaw",display=FALSE)
figNums(name="fitBA.plot",display=FALSE)
figNums(name="fitBApct.plot",display=FALSE)

>>>>

# Create a table for the appendix with growth rates
piDat.table<-
  dat %>% 
  mutate(TreeID=paste(Plot,TreeID,sep="-")) %>% # create unique treeID
  filter(TreeID %in% treeList) %>%
  filter(Year %in% c(1992,2019)) %>% 
  # mutate(BA=(DBH/2/100)^2*pi) %>% # convert DBH to basal area
  dplyr::select(Plot,TreeID,Species,Year,DBH) %>% 
  pivot_wider(names_from=Year,values_from=DBH) %>% 
  mutate(BA92=(`1992`/2/100)^2*pi) %>% 
  mutate(BA19=(`2019`/2/100)^2*pi) %>%
  mutate(PI=BA19-BA92) %>% # 
  filter(PI>0) %>%   # one tree has a PI of 0, has to be removed
  mutate(initDiam=`1992`) %>% 
  mutate(diamClass=cut(initDiam,breaks=c(7.5,12.5,18.5,30,90),include.lowest=T,right=F)) %>% 
  left_join(plotDat,by="Plot") %>% 
  mutate(BA.Target=paste("TU:",BA.Target,sep="")) %>%  # create facet column
  group_by(BA.Target,Species,diamClass) %>% 
  summarise(BAImean=mean(PI),
            BAIse=sd(PI)/sqrt(length(PI))) %>% 
  arrange(BA.Target,diamClass,Species)

@@

# Captions
appNums(name="piInitRaw",display=FALSE)
appNums(name="piPCTInitRaw",display=FALSE)
appNums(name="piDataRaw",display=FALSE)

figNums(name="fitBA.plot",display=FALSE)
figNums(name="fitBApct.plot",display=FALSE)
